Using an SMT engine to generate Symbolic Automata

### 2019-03-05 2017-Xudong-SMT/ActaInformatica.tex
added soem details in use-case

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{fig:ArchFailure:OA}
\end{figure}

Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
algorithm. For reasons of readability, we did not show the full
details of the open transitions on this figure. Below we list the
first 3 of them (full details available in \ref{RR}). 
This automaton has 12 transitions, including those encoding various
possible firing of some interactions (e.g. OT 2 and 3 for
{\PortFail}). It looks like the rough behaviour is
reasonable, although a detailed study shows that the property stated
above does not hold, because of the
{\PortFail} loops on states $11$ and $12$. This is because we did not
use the maximal progress assumption here. If we do, we get the
corrected behaviour in \fig{ArchFailure:OA-MaxProgress}
(\app{full-results}), in which $OT_7$ has disappeared, and $OT_2$ and
$OT_{10}$ have been restricted to $b0=\false$.

  \begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
  \caption{The open Automaton of the Failure Monitor Architecture,
    with Maximal Progress}
  \label{fig:ArchFailure:OA-MaxProgress}
  \end{figure}

  \TODO{Eric: Explain}

>>>>

%% CTL
\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{AF}#1}}
\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
\newcommand{\EX}[1][\ ]{\ensuremath{\mathtt{EX}#1}}
\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
\newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{XFIG/TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{fig:ArchFailure:OA}
\end{figure}

Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
algorithm. For reasons of readability, we did not show the full
details of the open transitions on this figure. Below we list the
first 3 of them (full details available in \ref{RR}). 
This automaton has 12 transitions, including those encoding various
possible firing of some interactions (e.g. OT 2 and 3 for
{\PortFail}). It looks like the rough behaviour is
reasonable, although a detailed study shows that the property stated
above does not hold, because of the
{\PortFail} loops on states $11$ and $12$. This is because we did not
use the maximal progress assumption here. If we do, we get the
corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
which $OT_7$ has disappeared, and $OT_2$ and 
$OT_{10}$ have been restricted to $b0=\false$.

\bigskip
\noindent
$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{init} \ostate{11}}
$

\medskip    
\noindent
$  OT_2  = \openrule
{\{B\mapsto fail(b0)\},\\
  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
  \{z:=z1\} }
{\ostate{11} \OTarrow{fail} \ostate{11}}
$
\medskip

\noindent
  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
    \{z:=z1\} }
  {\ostate{11} \OTarrow{fail} \ostate{12}}
  $
  \medskip

  \begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{XFIG/TimerOAMaxProgress}
  \caption{The open Automaton of the Failure Monitor Architecture,
    with Maximal Progress}
  \label{fig:ArchFailure:OA-MaxProgress}
  \end{figure}

  \TODO{Eric: Explain}
\begin{itemize}
\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
\item $OT_7$ has disappeared because it is now unsat.
\end{itemize}
